{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2018-01-10 thesis/landslide.tex
configure fonts

\chapter{Landslide}
\inspirationalquote{Somewhere is the promise of an uncharted trail, with 700 branching limbs and 700 ways to fail.}
{ThouShaltNot, ``Cardinal Directions''}

>>>>

\chapter{Landslide}
\inspirationalquote{Somewhere is the promise of an uncharted trail, with 700 branching limbs and 700 ways to fail.}
{ThouShaltNot, "Cardinal Directions"}

### 2018-01-10 thesis/thesis.tex
add fig:tree
add incomplete intro
rearrange some stuff bw intro/bgnd
add landslide chapt
configure fonts

% some useful packages
\usepackage[charter]{mathdesign}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[numbers,sort]{natbib}
\usepackage[backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfigure}

@@

Please hold on. This thesis will be departing shortly for the Landslide terminal, baggage claim, ground transportation, and ticketing.
\end{acknowledgments}

\tableofcontents
\listoffigures
\listoftables

\cleardoublepage
\pagestyle{empty}
\begin{center}
\begin{tabular}{c}
\vspace{12em} \\
\includegraphics[width=0.55\textwidth]{how-i-learned.png}
\end{tabular}
\end{center}

@@

\newcommand{\inspirationallinebreak}{\vspace{0.25em}}
\newcommand\inspirationalquote[2]{\begin{flushright}
	\vspace{-1em}
	\fontfamily{pzc}\selectfont
	{\em #1}
	\inspirationallinebreak

	---{#2}
	\fontfamily{mdbch}\selectfont
	\vspace{2em}
\end{flushright}}

\chapter{Introduction}

\input{background}

\chapter{Quicksand}
\inspirationalquote{Somewhere is the promise of an uncharted trail, with 700 branching limbs and 700 ways to fail.}
{ThouShaltNot, ``Cardinal Directions''}

@@

\chapter{Related Work}
\inspirationalquote{
\begin{tabular}{p{0.6\textwidth}}
To test if your paper makes a genuine contribution to its discipline,
see if you can afford a generous tone in the ``Related Work'' section.
\end{tabular}}
{Conor McBride, via Twitter}

\chapter{Conclusion}
\inspirationalquote{
%	``If you are a god, Zeus, as the stories claim, then why did you create evolution?
%	Why did you make \\ a world that can only grow through cruelty and pain?''
%	\inspirationallinebreak
%
%For a moment--surely this meant death was near--she thought she heard him answer:
%``My child, I \\
%was shaped by the gods that came before me, as you were shaped by me.
%The choice I had was be- \\
%tween creation and oblivion, life and death.
%And I chose life, because any life is better than no life, \\
%because as long as there is life, there is hope--if not for us, then for some generation to come.''
%	\inspirationallinebreak
%
%``Then how are you a god, if you can offer so little?'' she whispered, feeling death creep closer.
%	\inspirationallinebreak
%
%``I am a god because I take upon myself the burden of creation,'' the statue replied.
%	\inspirationallinebreak
%
%``Then we are all gods,'' Alexandra said, and pushed the button.}
	\begin{tabular}{p{0.875\textwidth}}
	``If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?''
	\\
	For a moment--surely this meant death was near--she thought she heard him answer:
	``My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope--if not for us, then for some generation to come.''
	\\
	``Then how are you a god, if you can offer so little?'' she whispered, feeling death creep closer.
	\\
	``I am a god because I take upon myself the burden of creation,'' the statue replied.
	\\
	``Then we are all gods,'' Alexandra said, and pushed the button.
	\end{tabular}}
{The Talos Principle: Road to Gehenna}

>>>>

% some useful packages
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[numbers,sort]{natbib}
\usepackage[backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfigure}
\usepackage{xspace}

%% custom fonts

\usepackage{fontspec}
\usepackage{xeCJK}

\setmainfont{XCharter}
%\setmainfont{Utopia}[
%	Path = ./fonts/,
%	UprightFont = UtopiaStd-Regular.otf,
%	BoldFont = UtopiaStd-Semibold.otf,
%	ItalicFont = UtopiaStd-Italic.otf,
%	BoldItalicFont = UtopiaStd-SemiboldIt.otf
%	]

\setCJKmainfont{HeiseiMinStd-W5}[Path = ./fonts/]

@@

I thank my dog, Louie.
\end{acknowledgments}

\tableofcontents
% TODO: figure out how to make latex abbreviate these
\listoffigures
\listoftables

@@

\newcommand{\inspirationallinebreak}{\vspace{0.25em}}
\newcommand{\inspirationalhyphen}{-\hspace{-0.15em}-\xspace}
\newcommand\inspirationalquote[2]{\begin{flushright}
	\vspace{-1em}
	{
	\fontspec[Path=./fonts/]{AlexaStd}
	{\em #1}
	\inspirationallinebreak

	-\hspace{-0.15em}-\hspace{-0.15em}-{#2}
	}
	\vspace{2em}
\end{flushright}}

\input{intro}
\input{background}
\input{landslide}

\chapter{Quicksand}

@@

\chapter{Related Work}
\inspirationalquote{
\begin{tabular}{p{0.58\textwidth}}
To test if your paper makes a genuine contribution to its discipline,
see if you can afford a generous tone in the "Related Work" section.
\end{tabular}}
{Conor McBride, via Twitter}

\chapter{Conclusion}
\inspirationalquote{
	\begin{tabular}{p{0.84\textwidth}}
	"If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?"
	\\
	For a moment\inspirationalhyphen{}surely this meant death was near\inspirationalhyphen{}she thought she heard him answer:
	"My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope\inspirationalhyphen{}if not for us, then for some generation to come."
	\\
	"Then how are you a god, if you can offer so little?" she whispered, feeling death creep closer.
	\\
	"I am a god because I take upon myself the burden of creation," the statue replied.
	\\
	"Then we are all gods," Alexandra said, and pushed the button.
	\end{tabular}}
{The Talos Principle: Road to Gehenna}
